Data Exploration

### 2018-11-26 src/data_exploration.Rmd
histograms of all env. correlates

just do surface layers for now

@@

>>>>

@@

chl
```{r}
hist(presence$chl_surface, main = "Chlorophyll at Surface", xlab = "Chlorophyll Concentrations (mmol.m-3)")
dev.copy(png, "../output/env/simple_plots/chl_surface_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
hist(presence$chl_depth, main = "Chlorophyll at Observation Depth", xlab = "Chlorophyll Concentrations (mmol.m-3)")
dev.copy(png, "../output/env/simple_plots/chl_depth_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

salinity
```{r}
hist(presence$salinity_surface, main = "Salinity at Surface", xlab = "Salinity Practical Salinity Unit (PSU)")
dev.copy(png, "../output/env/simple_plots/sal_surface_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
hist(presence$salinity_depth, main = "Salinity at Observation Depth", xlab = "Salinity Practical Salinity Unit (PSU)")
dev.copy(png, "../output/env/simple_plots/sal_depth_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

oxygen
```{r}
hist(presence$o2_surface, main = "Dissolved Oxygen at Surface", xlab = "Mole Concentration of Dissolved Oxygen in Sea Water (mmol.m-3)")
dev.copy(png, "../output/env/simple_plots/o2_surface_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
hist(presence$o2_depth, main = "Dissolved Oxygen at Observation Depth", xlab = "Mole Concentration of Dissolved Oxygen in Sea Water (mmol.m-3)")
dev.copy(png, "../output/env/simple_plots/o2_depth_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

MLP
```{r}
hist(presence$mlp, main = "Mixed Layer Thickness at Observation", xlab = "Mixed Layer Thickness (m)")
dev.copy(png, "../output/env/simple_plots/mlp_surface_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

ssh
```{r}
hist(presence$ssh, main = "Sea Surface Height at Observation", xlab = "Sea Surface Height (m)")
dev.copy(png, "../output/env/simple_plots/ssh_surface_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```
